{\boldmath Pseudoscalar top-Higgs coupling: Exploration of $\mathrm{CP}$-odd observables to resolve the sign ambiguity }

### 2016-03-10 Paper_ttbarH_Draft.tex
Small edits

\begin{abstract}
\vspace*{4mm} We present a collection of $\mathrm{CP}$-odd observables
for the process $\ppprocess$ that are linearly dependent on the scalar
($\kp$) and pseudoscalar ($\kpt$) top-Higgs coupling and hence
sensitive to the corresponding relative sign. The proposed observables
are based on triple product (TP) correlations that we extract
from the expression for the differential cross section in terms of the
spin vectors of the top and antitop quarks. In order to explore other
possibilities, we progressively modify these TPs, first
by combining them, and then by replacing the spin vectors by the
lepton momenta or the $t$ and $\tbar$ momenta by their visible parts.
We generate Monte Carlo data sets for several benchmark scenarios,
including the Standard Model ($\kp=1$, $\kpt=0$) and
two scenarios with mixed $\mathrm{CP}$ properties ($\kp=1$, $\kpt=\pm 1$).
{\bf (KK: worded correctly?)}
Assuming an integrated luminosity that is consistent with that
envisioned for the High Luminosity Large Hadron Collider,
and taking into account
only statistical uncertainties,
we find that the most
promising observable can disentangle the
``$\mathrm{CP}$-mixed'' scenarios 
with an effective separation of $\sim 20\sigma$.  In
the case of observables that do not require the reconstruction of the $t$
and $\tbar$ momenta, the power of discrimination is up to $\sim
16\sigma$ for the same number of events. We also show that the
most promising observables can still disentangle the
$\mathrm{CP}$-mixed scenarios when the number of events
is reduced to values consistent with expectations
for the Large Hadron Collider in the near term.

@@

The remainder of this paper is organized as follows. In
Sec.~\ref{sec2} we study the theoretical framework for the process
$\ppprocess$ and derive a general expression for the differential
cross section.  A first set of TP correlations is then
extracted from this expression.
In Sec.~\ref{sec3} we probe the sensitivity of these TPs to
the $tH$ coupling by using various $\mathrm{CP}$-odd
observables. Subsequent sections are dedicated to the analysis of
other $\mathrm{CP}$-odd observables. In particular,
observables based on TPs that incorporate the Higgs momentum
{\bf (KK: not all of them involve the Higgs momentum in this section\ldots
  is this the best way to describe this section?
  I'm fine with it, either way.)} are
discussed in Sec.~\ref{sec4}, and observables that do not
involve the $t$ and $\tbar$ momenta are studied in
Sec.~\ref{sec5}.  In Sec.~\ref{sec6} we discuss
the experimental feasibility of the most promising observables
encountered here. The main conclusions are summarized in
Sec.~\ref{sec7}.

@@

Using the expressions defined above for $\bar{\psi}_t$ and
$\psi_{\tbar}$, we can write the amplitude $\mathcal{M}^{ab,ij}$
in a form that is (in a sense) factorized.
As a first step, we insert
Eqs.~(\ref{eq7}) and (\ref{eq8}) into Eq.~(\ref{eq6}), yielding
%
\beq
\label{eq9}
\mathcal{M}^{ab,ij}=\!-g^4\,\mathbb{P}_t(t)\,\mathbb{P}_t(\tbar)\,\mathbb{P}_W(t-b)\,\mathbb{P}_W(\tbar-\bbar)\,\langle b-|\nu_{\ell}+\rangle \langle\nubar+|\bbar-\rangle \sqrt{\strut2(t\cdot {\ell}^+)}\sqrt{\strut2(\tbar\cdot {\ell}^-)}\,[\bar{\phi}_t \mathcal{A}^{ab,ij}\phi_{\tbar}],
%\frac{1}{(t^2-m^2_t+im_t\Gamma_t)}\,\frac{1}{(\tbar^2-m^2_t+im_t\Gamma_t)}\,\frac{1}{((t-b)^2-M^2_W)}\frac{1}{((\tbar-\bbar)^2-M^2_W)}\,\langle b-|\nu+\rangle\,\langle\nubar+|\bbar-\rangle
\eeq
%
where the spinors $\phi_{t}$ and $\phi_{\tbar}$ are defined as
%
\beq
\label{eq10}
\phi_t=\frac{(\tslash +m_t)}{\sqrt{\strut2(t\cdot {\ell}^+)}}|{\ell}^++\rangle
\eeq
%
\beq
\label{eq11}
\phi_{\tbar}=\frac{(\tbslash -m_t)}{\sqrt{\strut2(\tbar\cdot {\ell}^-)}}|{\ell}^-+\rangle \,.
\eeq
%
Note that in writing down the above expressions we have adopted the narrow-width
approximation for the top and antitop quarks and for the $W^\pm$ gauge
bosons{\bf (KK: remove ``\ldots and for the\ldots''?)}.\footnote{Since Eq.~(\ref{eq9}) contains the top quark propagator
  term
  $\mathbb{P}_t(t)$, for example, $|\mathcal{M}^{ab,ij}|^2$ contains
  the factor $((t^2-m^2_t)^2+m^2_t\Gamma^2_t)^{-1}$,
  which is replaced by $(\pi/m_t\Gamma_t)\delta(t^2-m^2_t)$
  in the narrow-width approximation.  Thus, except for the propagator terms $\mathbb{P}_t(t)$ and $\mathbb{P}_t(\tbar)$,
   we take the four-vector $t$ appearing in Eqs.~(\ref{eq9})-(\ref{eq11}) to be
  on shell, satisfying $t^2 = m_t^2$.} 
Working out the projection operators $\phi_t\,\bar{\phi}_t$
and $\phi_{\tbar}\,\bar{\phi}_{\tbar}$, we have
%
\beq
\label{eq12}
\phi_t\,\bar{\phi}_t=\frac{1}{2}(1+\nslash_{\!t}\gamma^5)(\tslash +m_t)
\eeq
%
and
%
\beq
\label{eq13}
\phi_{\tbar}\,\bar{\phi}_{\tbar}=\frac{1}{2}(1+\nslash_{\!\tbar}\gamma^5)(\tbslash -m_t),
\eeq
%
with $n_t$ and $n_{\tbar}$ being the four-vectors defined in
Eqs.~(\ref{eq3}) and (\ref{eq4}).  Thus, $\phi_t$ and $\phi_{\tbar}$
may be regarded as
describing a top quark with spin vector $n_t$ and an antitop quark
with spin vector $n_{\tbar}$, respectively.

@@

We have also tested various
linear combinations of the TPs $\epsilon_{1,2,3}$ and have found
that the asymmetry is enhanced for the following combination:
%
\beq
\setlength{\abovedisplayskip}{9.5pt}
\setlength{\belowdisplayskip}{9.5pt}
\label{eq24}
\epsilon_4=\epsilon_3-\epsilon_2=\epsilon(Q,t-\tbar,n_t,n_{\tbar}).
\eeq
%
Note that in the $Q$ rest frame, $\epsilon_4=Q^0
(\vec{t}-\vec{\tbar}\,)\cdot(\vec{n}_t\times \vec{n}_{\tbar})$ and the
sign of this TP is determined by the quantity
$(\vec{t}-\vec{\tbar}\,)\cdot(\vec{n}_t\times \vec{n}_{\tbar})$.
The
values obtained for the asymmetry associated with this TP are shown in
Table~\ref{table2}. By comparing the results in Tables~\ref{table1}
and \ref{table2}, we see that the capability of this
asymmetry to distinguish between the
two $\mathrm{CP}$-mixed scenarios is increased by at least $3\sigma$.
{\bf (KK: looks like 2.5$\sigma$ is the min difference?  maybe a rounding
  thing; but see also the comment in the table caption.)}
\vspace{4mm}
\begin{table}[H]
\caption{Asymmetry for the TP $\epsilon_{4}$ for the SM case and the
  two $\mathrm{CP}$-mixed scenarios.  The
  values are obtained using sets of $10^5$ simulated events.
{\bf (KK: In the previous table we used 3 sig figs for the ratios like ``12.0'', etc.  Should we do the same in both tables for consistency?)}}
\label{table2}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|====|}
%\hhline{|--------|}
$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_4)$~~&$\mathcal{A}(\epsilon_4)/\sigma_{\mathcal{A}}$ \\ 
\hhline{|====|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $-0.0371$~~~ & $-12$~~~ \\[0.6mm]
\hline
$1$ & $0$ & $0.0004$~ & $0.1$ \\[0.6mm]
\hline
$1$ & $1$ & $0.0461$~ & $14\,$ \\[0.6mm]
\hhline{|====|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
\par Finally, it is worth noting that the asymmetries
described in this subsection are not useful for
discriminating between the SM hypothesis ($\kp=1,\kpt=0$) and the pure
pseudoscalar hypothesis ($\kp=0,\kpt=1$).  Since
the numerators of the 
asymmetries are linear in both
$\kp$ and $\kpt$, they are expected to vanish in these cases. However, we
will show in the next subsection
that there exist angular distributions
derived from the TPs that are actually suitable for distinguishing between these
two hyphotheses.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Angular Distributions}
\label{sec3.2}

@@

In order to quantify the shifts discussed above, we have fitted
the simulated distributions with the following function, which was proposed in
Ref.~\cite{Ellis},
%
\beq
\label{eq27}
\frac{1}{\sigma}\frac{d\sigma}{d\Delta\phi_i(n_t,n_{\tbar})}=a_0 + a_1\cos(\Delta\phi_i(n_t,n_{\tbar})+\delta),\qquad\, i=1,2,3.
\eeq
%
To the extent that the above expression is exact, we note that
Eq.~(\ref{eq26}) 
gives $\mathcal{A}(\epsilon_i)=4a_1 \sin\delta$ {\bf (KK: sign
  incorrect? numbers don't agree between Tables I and III otherwise)}. With
this fitting function, we obtain phase shifts $\delta$ that
are approximately between
$0.9$ and $1$ ($-1$ and $-0.9$) for $\kp=\kpt=1$ ($\kp=-\kpt=1$), both
for $\epsilon_1$ and $\epsilon_2$.\footnote{The results for the
  TP $\epsilon_3$ are relatively similar to
  those for $\epsilon_2$, except that the phase shifts have the opposite
  sign in the $\mathrm{CP}$-mixed cases.  Given this similarity
  we do not include the corresponding results for the $\epsilon_3$ distribution
  here.}  However, the quality of the fits in the four scenarios considered is
not very good, particularly for $\epsilon_1$.  The
$\chi^2/\mathrm{d.o.f}$ for the fits corresponding to $\epsilon_1$ are in the range
$1.69$-$3.86$, while for $\epsilon_2$ they are in the range $0.53$-$1.16$.
The deviation from the functional
form proposed in Eq.~(\ref{eq27}) appears to be due primarily to the $\Delta
R_{ll}$ cut that we have imposed. In fact, when this cut is turned off, the
above ranges for the $\chi^2/\mathrm{d.o.f}$ become $0.75$-$1.14$ and
$0.44$-$1.07$ for the $\epsilon_1$ and $\epsilon_2$ distributions,
respectively. Tables \ref{table3} and \ref{table4} list the
results of the fits obtained when the $\Delta R_{\ell\ell}$ cut is
relaxed.  Figure~\ref{fig7} shows the corresponding
plots for a couple of the scenarios.
As is evident from Tables \ref{table3} and \ref{table4}, the
parameter $\delta$ is sensitive not only to the modulus of $\kpt$ but
also to its sign, as would be expected from Eq.~(\ref{eq26}).
The phase shift $\delta$ for the $\Delta\phi_1$ distribution
appears to exhibit a slightly higher sensitivity than
that obtained for the $\Delta\phi_2$ distribution, although the corresponding
numerical values obtained for the various scenarios are
compatible to within their statistical uncertainties. It is
important to stress, however, that the fits for the $\Delta\phi_2$ distributions
always yield smaller values for the $\chi^2/\mathrm{d.o.f}$.

@@

The results obtained for the TPs $\epsilon_1=
\epsilon(t,\tbar,n_t,n_{\tbar})$, $\epsilon_2=
\epsilon(Q,\tbar,n_t,n_{\tbar})$ and $\epsilon_3
=\epsilon(Q,t,n_t,n_{\tbar})$ introduced in Sec.~\ref{sec2} are
displayed in Table~\ref{table5}.  For each TP we list the 
mean value divided by the
corresponding statistical uncertainty.
%A deviation  of the estimator of $\langle
%\epsilon \rangle$, $\bar{\epsilon}$.
We see that the three observables are capable of distinguishing the SM
case from both $\mathrm{CP}$-mixed cases. Furthermore,
the two $\mathrm{CP}$-mixed cases
are clearly disentangled, since the the observables are
sensitive to the sign of $\kpt$. The observables $\langle \epsilon_2
\rangle$ and $\langle \epsilon_3 \rangle$ appear to be slightly more
sensitive than $\langle \epsilon_1 \rangle$.  Also, the
mean value for the combination $\epsilon_4$ introduced in
Sec.~\ref{sec3.1} gives slightly smaller values than those listed in
Table~\ref{table5} for $\langle \epsilon_2
\rangle$ and $\langle \epsilon_3 \rangle$,
       {\bf (KK: explicit reference to $\epsilon_2$ and $\epsilon_3$ correct?
         Seems like $\epsilon_4$ is actually a bit better than $\epsilon_1$)}
yielding $-4.32$, $1.11$ and $7.23$ for the cases
$(\kp=1,\kpt=-1,0,1)$, respectively. As with the asymmetry, the
purely $\mathrm{CP}$-even and purely $\mathrm{CP}$-odd cases cannot be
distinguished by the mean value, since it is linear in both $\kp$ and
$\kpt$ (see Eqs.~(\ref{eq20}) and (\ref{eq28})). Comparing the results
in Table~\ref{table5} with
the results presented in Sec.~\ref{sec3.1}, we can conclude that
the sensitivity to the NP contribution is smaller for the mean values
of the TPs under consideration
than for the corresponding asymmetries.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{{\boldmath $\mathrm{CP}$}-odd observables not depending on \MakeLowercase{{\boldmath $t$}} and \MakeLowercase{{\boldmath $\tbar$}} spin vectors}
\label{sec4}
So far we have considered three TPs involving the momenta $t,\tbar$
and $Q$ and the spin vectors $n_t$ and $n_{\tbar}$ [defined in
Eqs.~(\ref{eq3})-(\ref{eq4})].  Furthermore, we have described the general
form of the differential cross section in terms of these vectors in
Eq.~(\ref{eq20}). In this section we consider other
possibilities for the choice of the vectors from which the
$\mathrm{CP}$-odd observables can be constructed. From the definitions
in Eqs.~(\ref{eq3}) and (\ref{eq4}), we see that the TPs
$\epsilon_{1,2,3}$ can be written as follows,
%
\beq
\label{eq29}
\TPa = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\,\epsilon(t,\tbar,\ell^-\!,\ell^+),
\eeq
%
\vspace*{1mm}
\beq
\label{eq30}
\TPb = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\left(\epsilon(t,\tbar,\ell^-\!,\ell^+)+\epsilon(H,\tbar,\ell^-\!,\ell^+)+\frac{(t\cdot\ell^+)}{m^2_t}\epsilon(H,\tbar,t,\ell^-\!)\right) \,,
\eeq
%
\vspace*{1mm}
\beq
\label{eq31}
\TPc = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\left(-\epsilon(t,\tbar,\ell^-\!,\ell^+)+\epsilon(H,t,\ell^-\!,\ell^+)+\frac{(\tbar\cdot\ell^-)}{m^2_t}\epsilon(H,\tbar,t,\ell^+\!)\right).
\vspace*{2mm}
\eeq
%
The above equations express the TPs studied in the last sections as
linear combination of TPs involving the momenta $t,\tbar,H,\ell^+$ and
$\ell^-$, with coefficients that are functions of phase space
variables. These five momenta give rise to five TPs whose sensitivity
can also be tested by means of the observables introduced in
Secs.~\ref{sec3.1}-\ref{sec3.3}.  We have found
that TPs that do not include both the lepton and anti-lepton momenta yield
negligible sensitivity to the value of $\kpt$.  For this reason,
we concentrate here on the
results obtained for the remaining TPs,\footnote{These TPs should not be confused with those introduced in Eq.~(\ref{eq20}).}
%
\beq
\label{eqa5}
\epsilon_5\equiv\epsilon(t,\tbar,\ell^-\!,\ell^+) \,,
\vspace*{1mm}
\eeq
%
\beq
\label{eqa6}
\epsilon_6\equiv\epsilon(H,t,\ell^-\!,\ell^+) \,,
\vspace*{1mm}
\eeq
%
\beq
\label{eqa7}
\epsilon_7\equiv\epsilon(H,\tbar,\ell^-\!,\ell^+) \,.
\vspace*{1mm}
\eeq
%

@@

We have also proposed a combination of the TPs,
$\epsilon_4\equiv \epsilon_3-\epsilon_2$,
which has a greater sensitivity than $\epsilon_1$-$\epsilon_3$.
With $1\times 10^5$ events, for example, the asymmetry associated
with this TP gives an effective separation 
between the $\mathrm{CP}$-mixed scenarios that
exceeds those coming from $\epsilon_1$-$\epsilon_3$
by at least $3\sigma$. {\bf (KK: 2.5$\sigma$ is the min difference?)}   
When a similar
combination is constructed by using the leptons' momenta instead of the
spin vectors ($\epsilon_8$), the sensitivity in the asymmetry is
decreased by $\sim 3\sigma$ compared to the asymmetry associated
with $\epsilon_4$ for
the same number of events, giving values comparable with those
obtained for the asymmetries of $\epsilon_2$ and $\epsilon_3$. \par

>>>>

\begin{abstract}
\vspace*{4mm} We present a collection of $\mathrm{CP}$-odd observables
for the process $\ppprocess$ that are linearly dependent on the scalar
($\kp$) and pseudoscalar ($\kpt$) top-Higgs coupling and hence
sensitive to the corresponding relative sign. The proposed observables
are based on triple product (TP) correlations that we extract
from the expression for the differential cross section in terms of the
spin vectors of the top and antitop quarks. In order to explore other
possibilities, we progressively modify these TPs, first
by combining them, and then by replacing the spin vectors by the
lepton momenta or the $t$ and $\tbar$ momenta by their visible parts.
We generate Monte Carlo data sets for several benchmark scenarios,
including the Standard Model ($\kp=1$, $\kpt=0$) and
two scenarios with mixed $\mathrm{CP}$ properties ($\kp=1$, $\kpt=\pm 1$).
Assuming an integrated luminosity that is consistent with that
envisioned for the High Luminosity Large Hadron Collider,
and taking into account
only statistical uncertainties,
we find that the most
promising observable can disentangle the
``$\mathrm{CP}$-mixed'' scenarios 
with an effective separation of $\sim 20\sigma$ {\bf (N: In previous version it said ``statistical level" because we wanted 
to stress that we are not considering systematic uncertainties.)}.  In
the case of observables that do not require the reconstruction of the $t$
and $\tbar$ momenta, the power of discrimination is up to $\sim
16\sigma$ for the same number of events. We also show that the
most promising observables can still disentangle the
$\mathrm{CP}$-mixed scenarios when the number of events
is reduced to values consistent with expectations
for the Large Hadron Collider in the near term.

@@

The remainder of this paper is organized as follows. In
Sec.~\ref{sec2} we study the theoretical framework for the process
$\ppprocess$ and derive a general expression for the differential
cross section.  A first set of TP correlations is then
extracted from this expression.
In Sec.~\ref{sec3} we probe the sensitivity of these TPs to
the $tH$ coupling by using various $\mathrm{CP}$-odd
observables. Subsequent sections are dedicated to the analysis of
other $\mathrm{CP}$-odd observables. In particular,
observables based on TPs that {\bf (N: ``do not contain the $t$ and $\tbar$ spin vectors and
in certain cases incorporate")} the Higgs momentum
{\bf (KK: not all of them involve the Higgs momentum in this section\ldots
  is this the best way to describe this section?
  I'm fine with it, either way.)} are
discussed in Sec.~\ref{sec4} {\bf (N: ;)} and observables that do not
involve the $t$ and $\tbar$ momenta are studied in
Sec.~\ref{sec5}.  In Sec.~\ref{sec6} we discuss
the experimental feasibility of the most promising observables
encountered here. The main conclusions are summarized in
Sec.~\ref{sec7}.

@@

Using the expressions defined above for $\bar{\psi}_t$ and
$\psi_{\tbar}$, we can write the amplitude $\mathcal{M}^{ab,ij}$
in a form that is (in a sense) factorized.
As a first step, we insert
Eqs.~(\ref{eq7}) and (\ref{eq8}) into Eq.~(\ref{eq6}), yielding
%
\beq
\label{eq9}
\mathcal{M}^{ab,ij}=\!-g^4\,\mathbb{P}_t(t)\,\mathbb{P}_t(\tbar)\,\mathbb{P}_W(t-b)\,\mathbb{P}_W(\tbar-\bbar)\,\langle b-|\nu_{\ell}+\rangle \langle\nubar+|\bbar-\rangle \sqrt{\strut2(t\cdot {\ell}^+)}\sqrt{\strut2(\tbar\cdot {\ell}^-)}\,[\bar{\phi}_t \mathcal{A}^{ab,ij}\phi_{\tbar}],
%\frac{1}{(t^2-m^2_t+im_t\Gamma_t)}\,\frac{1}{(\tbar^2-m^2_t+im_t\Gamma_t)}\,\frac{1}{((t-b)^2-M^2_W)}\frac{1}{((\tbar-\bbar)^2-M^2_W)}\,\langle b-|\nu+\rangle\,\langle\nubar+|\bbar-\rangle
\eeq
%
where the spinors $\phi_{t}$ and $\phi_{\tbar}$ are defined as
%
\beq
\label{eq10}
\phi_t=\frac{(\tslash +m_t)}{\sqrt{\strut2(t\cdot {\ell}^+)}}|{\ell}^++\rangle
\eeq
%
\beq
\label{eq11}
\phi_{\tbar}=\frac{(\tbslash -m_t)}{\sqrt{\strut2(\tbar\cdot {\ell}^-)}}|{\ell}^-+\rangle \,.
\eeq
%
Note that in writing down the above expressions we have adopted the narrow-width
approximation for the top and antitop quarks.\footnote{Since Eq.~(\ref{eq9}) contains the top quark propagator
  term
  $\mathbb{P}_t(t)$, for example, $|\mathcal{M}^{ab,ij}|^2$ contains
  the factor $((t^2-m^2_t)^2+m^2_t\Gamma^2_t)^{-1}$,
  which is replaced by $(\pi/(m_t\Gamma_t))\delta(t^2-m^2_t)$
  in the narrow-width approximation.  Thus, except for the propagator terms $\mathbb{P}_t(t)$ and $\mathbb{P}_t(\tbar)$,
   we take the four-vector $t$ appearing in Eqs.~(\ref{eq9})-(\ref{eq11}) to be
  on shell, satisfying $t^2 = m_t^2$.} 
Working out the projection operators $\phi_t\,\bar{\phi}_t$
and $\phi_{\tbar}\,\bar{\phi}_{\tbar}$, we have
%
\beq
\label{eq12}
\phi_t\,\bar{\phi}_t=\frac{1}{2}(1+\nslash_{\!t}\gamma^5)(\tslash +m_t)
\eeq
%
and
%
\beq
\label{eq13}
\phi_{\tbar}\,\bar{\phi}_{\tbar}=\frac{1}{2}(1+\nslash_{\!\tbar}\gamma^5)(\tbslash -m_t),
\eeq
%
with $n_t$ and $n_{\tbar}$ being the four-vectors defined in
Eqs.~(\ref{eq3}) and (\ref{eq4}).  Thus, $\phi_t$ and $\phi_{\tbar}$
may be regarded as
describing a top quark with spin vector $n_t$ and an antitop quark
with spin vector $n_{\tbar}$, respectively.

@@

We have also tested various combinations of the TPs $\epsilon_{1,2,3}$ and have found
that the asymmetry is enhanced for the following combination:
%
\beq
\setlength{\abovedisplayskip}{9.5pt}
\setlength{\belowdisplayskip}{9.5pt}
\label{eq24}
\epsilon_4=\epsilon_3-\epsilon_2=\epsilon(Q,t-\tbar,n_t,n_{\tbar}).
\eeq
%
Note that in the $Q$ rest frame, $\epsilon_4=Q^0
(\vec{t}-\vec{\tbar}\,)\cdot(\vec{n}_t\times \vec{n}_{\tbar})$ and the
sign of this TP is determined by the quantity
$(\vec{t}-\vec{\tbar}\,)\cdot(\vec{n}_t\times \vec{n}_{\tbar})$.
The
values obtained for the asymmetry associated with this TP are shown in
Table~\ref{table2}. By comparing the results in Tables~\ref{table1}
and \ref{table2}, we see that the capability of this
asymmetry to distinguish between the
two $\mathrm{CP}$-mixed scenarios is increased by at least $2.8\sigma$.
\vspace{4mm}
\begin{table}[H]
\caption{Asymmetry for the TP $\epsilon_{4}$ for the SM case and the
  two $\mathrm{CP}$-mixed scenarios.  The
  values are obtained using sets of $10^5$ simulated events.
}
\label{table2}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|====|}
%\hhline{|--------|}
$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_4)$~~&$\mathcal{A}(\epsilon_4)/\sigma_{\mathcal{A}}$ \\ 
\hhline{|====|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $-0.0371$~~~ & $-11.7$~~ \\[0.6mm]
\hline
$1$ & $0$ & $0.0004$~ & $0.1$ \\[0.6mm]
\hline
$1$ & $1$ & $0.0461$~ & $14.6$ \\[0.6mm]
\hhline{|====|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
\par Finally, it is worth noting that the asymmetries
described in this subsection are not useful for
discriminating between the SM hypothesis ($\kp=1,\kpt=0$) and the pure
pseudoscalar hypothesis ($\kp=0,\kpt=1$).  Since
the numerators of the 
asymmetries are linear in both
$\kp$ and $\kpt$, they are expected to vanish in these cases. However, we
will show in the next subsection
that there exist angular distributions
derived from the TPs that are actually suitable for distinguishing between these
two hyphotheses.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Angular Distributions}
\label{sec3.2}

@@

In order to quantify the shifts discussed above, we have fitted
the simulated distributions with the following function, which was proposed in
Ref.~\cite{Ellis},
%
\beq
\label{eq27}
\frac{1}{\sigma}\frac{d\sigma}{d\Delta\phi_i(n_t,n_{\tbar})}=a_0 + a_1\cos(\Delta\phi_i(n_t,n_{\tbar})+\delta),\qquad\, i=1,2,3.
\eeq
%
To the extent that the above expression is exact, we note that
Eq.~(\ref{eq26}) 
gives $\mathcal{A}(\epsilon_i)=-4a_1 \sin\delta$. With
this fitting function, we obtain phase shifts $\delta$ that
are approximately between
$0.9$ and $1$ ($-1$ and $-0.9$) for $\kp=\kpt=1$ ($\kp=-\kpt=1$), both
for $\epsilon_1$ and $\epsilon_2$.\footnote{The results for the
  TP $\epsilon_3$ are relatively similar to
  those for $\epsilon_2$, except that the phase shifts have the opposite
  sign in the $\mathrm{CP}$-mixed cases.  Given this similarity
  we do not include the corresponding results for the $\epsilon_3$ distribution
  here.}  However, the quality of the fits in the four scenarios considered is
not very good, particularly for $\epsilon_1$.  The
$\chi^2/\mathrm{d.o.f}$ for the fits corresponding to $\epsilon_1$ are in the range
$1.69$-$3.86$, while for $\epsilon_2$ they are in the range $0.53$-$1.16$.
The deviation from the functional
form proposed in Eq.~(\ref{eq27}) appears to be due primarily to the $\Delta
R_{ll}$ cut that we have imposed. In fact, when this cut is turned off, the
above ranges for the $\chi^2/\mathrm{d.o.f}$ become $0.75$-$1.14$ and
$0.44$-$1.07$ for the $\epsilon_1$ and $\epsilon_2$ distributions,
respectively. Tables \ref{table3} and \ref{table4} list the
results of the fits obtained when the $\Delta R_{\ell\ell}$ cut is
relaxed.  Figure~\ref{fig7} shows the corresponding
plots for a couple of the scenarios.
As is evident from Tables \ref{table3} and \ref{table4}, the
parameter $\delta$ is sensitive not only to the modulus of $\kpt$ but
also to its sign, as would be expected from Eq.~(\ref{eq26}).
The phase shift $\delta$ for the $\Delta\phi_1$ distribution
appears to exhibit a slightly higher sensitivity than
that obtained for the $\Delta\phi_2$ distribution, although the corresponding
numerical values obtained for the various scenarios are
compatible to within their statistical uncertainties. It is
important to stress, however, that the fits for the $\Delta\phi_2$ distributions
always yield smaller values for the $\chi^2/\mathrm{d.o.f}$.

@@

The results obtained for the TPs $\epsilon_1=
\epsilon(t,\tbar,n_t,n_{\tbar})$, $\epsilon_2=
\epsilon(Q,\tbar,n_t,n_{\tbar})$ and $\epsilon_3
=\epsilon(Q,t,n_t,n_{\tbar})$ introduced in Sec.~\ref{sec2} are
displayed in Table~\ref{table5}.  For each TP we list the 
mean value divided by the
corresponding statistical uncertainty.
%A deviation  of the estimator of $\langle
%\epsilon \rangle$, $\bar{\epsilon}$.
We see that the three observables are capable of distinguishing the SM
case from both $\mathrm{CP}$-mixed cases. Furthermore,
the two $\mathrm{CP}$-mixed cases
are clearly disentangled, since the the observables are
sensitive to the sign of $\kpt$. The observables $\langle \epsilon_2
\rangle$ and $\langle \epsilon_3 \rangle$ appear to be slightly more
sensitive than $\langle \epsilon_1 \rangle$.  Also, the
mean value for the combination $\epsilon_4$ introduced in
Sec.~\ref{sec3.1} gives slightly smaller values than those listed in
Table~\ref{table5} for $\langle \epsilon_2
\rangle$ and $\langle \epsilon_3 \rangle$,
       {\bf (KK: explicit reference to $\epsilon_2$ and $\epsilon_3$ correct?
         Seems like $\epsilon_4$ is actually a bit better than $\epsilon_1$) (N: The effective separation
         for $\epsilon_4$ is $11.55$ while for $\epsilon_1$ is $12.24$)}
yielding $-4.32$, $1.11$ and $7.23$ for the cases
$(\kp=1,\kpt=-1,0,1)$, respectively. As with the asymmetry, the
purely $\mathrm{CP}$-even and purely $\mathrm{CP}$-odd cases cannot be
distinguished by the mean value, since it is linear in both $\kp$ and
$\kpt$ (see Eqs.~(\ref{eq20}) and (\ref{eq28})). Comparing the results
in Table~\ref{table5} with
the results presented in Sec.~\ref{sec3.1}, we can conclude that
the sensitivity to the NP contribution is smaller for the mean values
of the TPs under consideration
than for the corresponding asymmetries.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{{\boldmath $\mathrm{CP}$}-odd observables not depending on \MakeLowercase{{\boldmath $t$}} and \MakeLowercase{{\boldmath $\tbar$}} spin vectors}
\label{sec4}
So far we have considered three TPs involving the momenta $t,\tbar$
and $Q$ and the spin vectors $n_t$ and $n_{\tbar}$ [defined in
Eqs.~(\ref{eq3})-(\ref{eq4})].  Furthermore, we have described the general
form of the differential cross section in terms of these vectors in
Eq.~(\ref{eq20}). In this section we consider other
possibilities for the choice of the vectors from which the
$\mathrm{CP}$-odd observables can be constructed. From the definitions
in Eqs.~(\ref{eq3}) and (\ref{eq4}), we see that the TPs
$\epsilon_{1,2,3}$ can be written as follows,
%
\beq
\label{eq29}
\TPa = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\,\epsilon(t,\tbar,\ell^-\!,\ell^+),
\eeq
%
\vspace*{1mm}
\beq
\label{eq30}
\TPb = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\left(\epsilon(t,\tbar,\ell^-\!,\ell^+)+\epsilon(H,\tbar,\ell^-\!,\ell^+)+\frac{(t\cdot\ell^+)}{m^2_t}\epsilon(H,\tbar,t,\ell^-\!)\right) \,,
\eeq
%
\vspace*{1mm}
\beq
\label{eq31}
\TPc = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\left(-\epsilon(t,\tbar,\ell^-\!,\ell^+)+\epsilon(H,t,\ell^-\!,\ell^+)+\frac{(\tbar\cdot\ell^-)}{m^2_t}\epsilon(H,\tbar,t,\ell^+\!)\right).
\vspace*{2mm}
\eeq
%
The above equations express the TPs studied in the last sections as
a combination of TPs involving the momenta $t,\tbar,H,\ell^+$ and
$\ell^-$, with coefficients that are functions of phase space
variables. These five momenta give rise to five TPs whose sensitivity
can also be tested by means of the observables introduced in
Secs.~\ref{sec3.1}-\ref{sec3.3}.  We have found
that TPs that do not include both the lepton and anti-lepton momenta yield
negligible sensitivity to the value of $\kpt$.  For this reason,
we concentrate here on the
results obtained for the remaining TPs,\footnote{These TPs should not be confused with those introduced in Eq.~(\ref{eq20}).}
%
\beq
\label{eqa5}
\epsilon_5\equiv\epsilon(t,\tbar,\ell^-\!,\ell^+) \,,
\vspace*{1mm}
\eeq
%
\beq
\label{eqa6}
\epsilon_6\equiv\epsilon(H,t,\ell^-\!,\ell^+) \,,
\vspace*{1mm}
\eeq
%
\beq
\label{eqa7}
\epsilon_7\equiv\epsilon(H,\tbar,\ell^-\!,\ell^+) \,.
\vspace*{1mm}
\eeq
%

@@

We have also proposed a combination of the TPs,
$\epsilon_4\equiv \epsilon_3-\epsilon_2$,
which has a greater sensitivity than $\epsilon_1$-$\epsilon_3$.
With $1\times 10^5$ events, for example, the asymmetry associated
with this TP gives an effective separation 
between the $\mathrm{CP}$-mixed scenarios that
exceeds those coming from $\epsilon_1$-$\epsilon_3$
by at least $2.8\sigma$.  
When a similar
combination is constructed by using the leptons' momenta instead of the
spin vectors ($\epsilon_8$), the sensitivity in the asymmetry is
decreased by $\sim 3.1\sigma$ compared to the asymmetry associated
with $\epsilon_4$ for
the same number of events, giving values comparable with those
obtained for the asymmetries of $\epsilon_2$ and $\epsilon_3$. \par
